### 2019-09-16 2019_neurips_vigil/experiments.tex
polishing experiment section

We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.  The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths.  The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.  Therefore, the memory is updated efficiently instead of storing all information across all frames.

@@

\begin{figure}
	\centering
	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset. We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard. }
	\resizebox{6cm}{3.5cm}{%

>>>>

We argue that the generalization capability of SAMNet is mainly due to the dynamic frame-by-frame processing of the input sequence.  The mechanisms introduced in SAMCell (e.g., Memory retrieval and update units) learn to operate independent of the total number of frames and allow to generalize to longer video lengths. As shown in Figure 3, when trained on the easy dataset, SAMNet still performs 91.6\% when tested on the hard dataset, whereas COG drops from 97.6\% to 65.9\%   The visualization of the trained SAMNet model (see Appendix) indicates that the model learns the concept of time, helping it to control the flow of information from visual input to the memory.  Therefore, the memory is updated efficiently instead of storing all information across all frames.

@@

\begin{figure}
	\centering
	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset. We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard. }
	\resizebox{6cm}{4.5cm}{%
